On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-27 Manuscript/manuscript.tex
Attempt at Explaining Copula

The simulation design was the same, except the target parameters of $W_t$ were:
1) $\mu = 1$, the mean of $W_t$;
2) $\sigma_w = 1$, the standard deviation of $W_t$; and
3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$
Although we may have set $\phi$ to these five levels for $X_t$: 
$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
the new five autocorrelation coefficients for $W_t$ will be different.
\mc{I may need some help explaining the calibration of copula parameters}
After calibrating the copula parameters using the \textsl{copula} and 
\textsl{pracma} packages, \citep{copula, pracma} we can again plot empirical coverage 
rates and the 95\% confidence intervals of the real coverage.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_rho}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient $\rho$ of an AR(1) process with
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_phi}
\end{figure}

>>>>

The simulation design was the same, except the target parameters of $W_t$ were:
1) $\mu = 1$, the mean of $W_t$;
2) $\sigma_w = 1$, the standard deviation of $W_t$; and
3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$
Although we may have set $\phi$ to these five levels for $X_t$: 
$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
the new five true autocorrelation coefficients for $W_t$ were different.
\mc{I may need some help explaining the calibration of copula parameters}
To calibrate the copula parameters, we first constructed a multivariate
exponential distribution from a normal copula using the \textsl{copula} package.
\citep{copula} Then we computed $E[XY]$, which 
requires double integration using the \textsl{pracma} package. \citep{pracma} 
Finally, we obtained true $\rho = E[XY] - 1$, which was used as the target
parameter when evaluating CI performance when estimating $\rho$.
After this step, we again plotted empirical coverage 
rates for $\mu$, $\sigma$, and $\rho$, as well as 95\% confidence intervals of 
the real coverage. These are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_rho}}.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_rho}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient $\rho$ of an AR(1) process with
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ transformed to
    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_rho}
\end{figure}
